\section{Closed-loop Model Checking}
%We first define the behavior space of a model as all combinations of states valuations. For a model $M$ with $n$ state variables $v_1\dots v_n$, and each state variable can take value within the domain $D(v_i)$, the size of the overall behavior space is $\Pi_{i=1}^n D(v_i)$. The actual reachable behavior space of a model $M$ is far less and can be defined by $\mathbb{B}(M)$. As a reference or ground truth for behavior space, we assume the behavior space $\mathbb{B}(S)$ for a physical system $S$ which is infinitely large. All the behavior spaces correspond to the models $\mathbb{B}(M)$ of the system are projections from $\mathbb{B}(S)$.  
%\Hao{}
For a model $M$ with state space $S$, we define the behavior of the system as an execution trace in $\delta\in S^*$. The reachable behavior space of model $M$ is denoted as $\mathbb{B}(M)\subset S^*$.

An abstraction function $h$ is a surjection from

No models of the system can match the region of the system exactly due to lack of information. As the model becomes more abstract, the boundary defining the behavior region becomes less complex. If the abstract model covers all the system behaviors such that $\mathbb{B}(S)\subset\mathbb{B}(M)$, the model is referred to as an \emph{over-approximation} of the system. For environment model, over-approximation can also be used to \emph{generalize} different environmental conditions, i.e. in \figref{distinction}.(a) two system behaviors $\mathbb{B}(S_1)$ and $\mathbb{B}(S_2)$ are covered by a model $\mathbb{B}(M)$.

A property defines a region in the behavior space within which the property is satisfied. The satisfaction region of a property $\varphi$ can be denoted as $\mathbb{B}(\varphi)$. 
A system $S$ satisfies a property $\varphi$ if $\mathbb{B}(S)\subseteq \mathbb{B}(\varphi)$. We denote it as $S\models\varphi$. As we can see, if $M$ is an over-approximation of $S$, meaning $\mathbb{B}(S)\subseteq \mathbb{B}(M)$, and $\mathbb{B}(M)\subseteq \mathbb{B}(\varphi)$, we have $\mathbb{B}(S)\subseteq \mathbb{B}(\varphi)$, meaning $S\models\varphi$. 

In most of the cases, the internal states and transitions of a system cannot be fully observable. The behavior space can thus be mapped to other observable behavior spaces with less dimensions.
\Hao{Need to clarify/visualize the notion of observability here} 
Note that the observability does not refer to the interface of the system, there can be multiple observable behavior spaces that correspond to different abstraction of the system. As the result, behaviors that are distinguishable in the full behavior space can be indistinguishable in a observable behavior space, causing ambiguities that can result in false-negatives and false-positives during verification. We denote one observable behavior space as $\mathbb{B}_o(S)$. 

As shown in \figref{distinction}, $\mathbb{B}(M)$ and $\mathbb{B}(\varphi)$ are mapped to $\mathbb{B}_o(M')$ and $\mathbb{B}_o(\varphi')$. Three behaviors in $b_1,b_2,b_3\in\mathbb{B}$ are mapped to a single behavior $b'\in\mathbb{B}_o$. Since $b'\not\in\mathbb{B}_o(\varphi')$, it may be returned by verification tools like model checker as counter-example. In $\mathbb{B}_o$ is possible that two categories of ambiguities exist, namely \textbf{Validity ambiguity} and \textbf{Context ambiguity}. %Failure to distinguish these behaviors can cause false-negatives and/or false-positives during verification.

Validity ambiguity refers to the incapability to distinguish a physically possible execution with an invalid one. In \figref{distinction}.(a), $b_3$ is an invalid behavior since it does not belong to either $S_1$ or $S_2$ but it is covered by the model $M$. 

A model $M$ is compatible with an observable behavior space $\mathbb{S}^o$ if all the behaviors that can be generated by $M$ 

A model is appropriate for a property if all its behaviors  



A Counter-Example-Guided Abstraction and Refinement approach has been proposed to automatically derive model with appropriate amount of details. (\cite{CEGAR}) Assume we would like to check the system $S$ against the property $\varphi$. First, the most abstract model $M_0\models^a S$ is derived from the actual system $S$ based on certain abstraction rules, so that it can distinguish all execution paths that satisfy/violate $\varphi$. Then $M_0$ is verified against the property in an automated model checker. If the property is violated $M_0\not\models\varphi$, a counter-example $\delta^c$ is returned by the model checker. $\delta^c$ has to be then validated so that it can be produced by $S$. If the system can produce $\delta^c$, which can be denoted as $\delta^c\triangleleft S$, $\delta^c$ is a valid counter-example. Otherwise $\delta^c$ is regarded as \textbf{spurious} and the model has to be refined so that the $\delta^c$ is not producible by the model. The refined model $M_1\models^a M_0$ is derived by adding back the minimum amount of abstracted details that prevent $\delta^c$ from being enabled, so that $\delta^c\not\triangleleft M_1$. This process continues until either no counter-example is returned, or a counter-example is not spurious. 

CEGAR works very well during system modeling in which there is only one concrete system implementation $S$. However, for closed-loop verification the objective is to check whether $E||S\models\varphi$. If the environment $E$ is also represented by a model during model checking, both $M^E$ and $M^S$ have to be unambiguous. When verifying system specifications, normally there is no constraints on the environment so that there is no spurious counter-examples due to the environment model. In this case CEGAR still works. However in the software requirements, there are constraints on the environment conditions. If these constraints are not enforced in $M^E$, the verification can yield spurious counter-examples. However, CEGAR will not work for environment modeling due to the differences between the environment and the system. In system modeling, there is only one concrete implementation $S$, so if a counter-example $\delta^c$ is returned during model checking, only $\delta^c\triangleleft S$ has to be checked. However, for the environment, there are infinite number of environmental conditions $E_i$, like different patients in the medical device domain. Details are ignored in the abstract models not only to reduce complexity, but also to \textbf{generalize} different conditions so that:
$$\forall \delta\triangleleft E_i, i\in [1,n],\delta\triangleleft M^E$$
Note that during the generalization process, more behaviors of the environment will be introduced into the model: 
$$\exists\delta^s\triangleleft M^E \text{ s.t. } \delta^s\not\triangleleft E_i, i\in [1,n]$$
In this case, if an execution path $\delta$ is returned as a counter-example during model checking on software requirement, there is no way to check whether 
$$\exists i\in[1,n],\delta\triangleleft E_i$$ 
as $n$ may be a large number or is unclear in the first place. As a result, the validity of the counter-example cannot be validated, and therefore the model cannot be refined by analyzing the spurious counter-example. CEGAR is not effective during environment modeling.

In Cyber-Physical Systems, there are \textbf{domain experts} who understand how the environment of the system works. The \textbf{domain knowledge} is a set of environmental constraints which can be used to define different environment conditions, and determine the validity of the execution paths. However, domain knowledge are in general not formalized thus cannot be used in any automated processes. In this paper, we use closed-loop model checking on an implantable pacemaker model as example to demonstrate abstraction and refinement of the environment models using encoding domain knowledge. We use two case studies to demonstrate that although CEGAR is not applicable to the environment model, the domain knowledge can still be used to validate executions and provide potential validity violations.\Hao{Still need to formalize}

The contribution of this paper is two-folds: 1) we formally specified the potential ambiguities during model abstraction and identified the difference between environment modeling and system modeling. 2) We demonstrated the potential application of encoded domain knowledge to eliminate the ambiguities during abstraction and refinement of environment models.
\begin{itemize}
	\item Abstraction rules for environment models 
    \item Appropriate abstraction function check, definition clear, assumptions implicit, especially for environment models
\end{itemize}