\documentclass[11pt, oneside, reqno]{article}
\usepackage{amssymb, amsthm, amsmath, amsfonts}
%\parindent=0pt

\newcommand\bs{\char '134 }
\newcommand{\Gc}{\mathcal{G}}
\newcommand{\Lc}{\mathcal{L}}
\newcommand{\Ic}{\mathcal{I}}
\newcommand{\Kc}{\mathcal{K}}
\newcommand{\Ne}{\mathbb{N}}
\newcommand{\Rc}{\mathcal{R}}


\begin{document}

\title{Automatic application of interdependent abstraction rules}
\author{Houssam Abbas}
\date{\today}
\maketitle

%\newpage
%\tableofcontents        
%\newpage

\section{Introduction}
Given a model of a system, a requirement $\varphi$, and a set of abstraction rules, we seek an automatic way to obtain the most abstract model of the system that is compatible with $\varphi$.
A model is \emph{compatible} with a spec if the truth value of the spec can be evaluated on any run of the model.
In particular, this requires that the atomic propositions of $\varphi$ refer to signals that are produced by the model.

\section{Representing abstraction rules}
We are given a finite directed graph $G=(V,E)$ representing the human heart. 
Each edge is a conduction path, and each vertex is a node.
Each vertex $v$ is decorated with an extended timed automaton $A_v$.
The expressions of invariants and guards of the automaton use a set of parameters $P_v$. 
These parameters can be reset at transitions of the automaton.
%Collectively, we refer to $(A_v,P_v,\Ic_v)$ as the dynamics $D_v$ of the vertex $v$.
Similarly, each edge $e$ is associated with an extended timed automaton $A_e$.
All vertex automata have one of 2 structures, and all path automata have the same structure. 
The differences between them are in the values of the parameters.

Let $I(G)$ be the set of all induced subgraphs of $G$, and $\Gc$ be the set of all finite directed graphs.
In what follows, all subgraphs are induced by $G$ unless stated otherwise.
Given subgraph $K$, $P_K$ is the parameter vector of all vertices and edges of $K$: $P_K = (P_x)_{x \in E(K) \cup V(K)}$.
For the rest of this document, fix the graph $G$.

A \emph{rule} $R$ is a partial function on the set $\Gc$ of finite directed subgraphs:
\[R: \Gc \rightarrow \Gc\]
The argument of $R$ might be all of $G$.
The rule has the following effect
\begin{itemize}
	\item $|V(R(K))| \leq |V(K)|$,
	\item $|E(R(K))| \leq |E(K)|$,
	\item $V(R(K)) \subset V(K)$,
	\item For every $v \in V(K) \cap V(R(K))$, $R(A_v)$ is an abstraction of $A_v$, in the sense that $\Lc(R(A_v))$ is a superset of $\Lc(A_v)$.
\end{itemize}
\emph{Informally}, the rule $R$ operates by one of four ways: deleting a vertex and all edges incident on it, deleting an edge, merging two vertices together, fusing two edges if the vertex they share has degree 2.
With each of these effects, the rule will also modify the \emph{parameter values} of the automata decorating some of the elements of the subgraph to which it applies.
abstracting (in the sense of behavior inclusion) the automaton decorating a vertex or edge, over-approximating the intervals decorating a vertex or edge.
A rule does NOT modify the structure of the automata.
Let $\Rc$ be the set of all rules we are concerned with.

\subsection{Rule applicability}
\label{ruleApplicability}
Each rule $R$ is associated with a subgraph $H_R = (V_R,E_R)$ and formula $\phi_R$ carrying on the parameters of $H_R$.
A rule is defined on a subgraph $K$ only iff $K$ is isomorphic to $H_R$ and its parameters satisfy $\phi_R$
\begin{equation}
\label{eq:applicableR}
R(K) \textrm{ is defined iff } K \equiv H_R \land P_K \models \phi_R
\end{equation}
E.g., Rule $R_1$ applies only on linear graphs with 3 vertices and whose parameters $ERP$ obey $ERP(v_1) < ERP(v_2)$ and $ERP(v_2) > ERP(v_3)$.\footnote{A cleaner, but perhaps less intuitive, way of doing this is by defining $R$'s domain to be the set of equivalence classes of $G$ induced by the isomorphism-to-$H_R$ relation. 
	That is, $R: I(G)/H_R  \rightarrow \Gc$ where $I(G)/H_R = \{C_1,C_2\}$ is the set of equivalence classes $C_1 = \{K \in I(G) \;|\; K \equiv H_R \}$ and $C_2 = \{K \in I(G) \;|\; K \not \equiv H_R\}$.
}

We assume that $\phi_R$ is given by linear predicates over $P$
\begin{equation}
\label{eq:formOfPhi}
\exists B_i, C_i\; s.t. P_K \models \phi_R \textrm{ iff } B_i P_K \leq C_i
\end{equation}

If a given subgraph is not of the form on which $R$ is applicable, then $R$ is not defined on it.
In what follows, we let $\Kc$ be the set of all induced subgraphs of $G$ that are isomorphic to some $H_{R}, R \in \Rc$ : $\Kc = \{K \in I(G) \; s.t. \; \exists R \in \Rc . K \equiv H_R\}$.

In a given $H_R$ (treated as the equivalence class of all subgraphs isomorphic to it), we may uniquely identify its vertices and the edges by numbering them in an increasing sequence.
We call the integer associated with a vertex or edge the \emph{role} played by that element in $H_R$.
E.g. given the linear graph $v e v' e' v''$, 
role($v$) = 0, role($v'$) = 1, role($v''$) = 2, role($e$) = 3, role($e'$) = 4.
When we determine that $K$ is isomorphic to $H_R$, the vertices and edges of $K$ are assigned the same roles as their isomorphic counterparts in $H_R$.
We call the elements of a subgraph $H_R$ \emph{co-actors} in the rule $R$, since they share the same stage $H_R$.

%As a matter of notational convenience, given rules $\Rc = \{R_1,\ldots,R_m\}$, we label the vertices of $H_{R_i}$ incrementally to avoid excessive book-keeping, i.e. no two vertices have the same role.
%\[\textrm{role}(v) \neq \textrm{role}(v') \; \forall v,v', v \in V(H_{R}), v' \in V(H_{R'}), R \neq R' \in \Rc\]
%Let $O \in \Ne$ be the highest role of any vertex in the graphs of $\Rc$:
%\[O = \max_{x \in \cup_{R \in \Rc} V(H_R)\cup E(H_R)} \textrm{role}(x)\]

\subsection{Rule effect}
\label{ruleEffect}
When a rule is applied on a subgraph $K$, its effect on a vertex $v \in V(K)$ depends on the role played by $v$ in $K$. 
E.g. in $H_R = v e v' e' v''$ and $K = v_1 e v_2 e' v_3$, assume that $R$ deletes the middle vertex $v'$, so $R(H_R) =  v e^+ v''$ (where $e^+$ is obtained by fusing $e$ and $e'$ together).
To know how $R$ affects $v_2$ we need to know what its role is.
Because role($v_2$) = role($v'$), we know that $v_2$ will be deleted. 
On the other hand, because role($v_1$) = role($v$) and $v$ is untouched, we know $v_1$ is untouched.

Given a graph $G = (V,E)$, a finite set of rules $\Rc = \{R_1,\ldots,R_m\}$, we have a choice of the order in which to apply the rules on $G$, and at each step (= each rule application), a choice of the induced subgraph on which to apply it.
Thus when we speak of applying a rule, we must give the rule $R_i$, the time step $j$ at which it is applied, and the particular subgraph $K$ to which it is being applied.
The boolean variable $a_{ijs}$ tracks that: it is 1 iff rule $R_i$ is applied at step $j$ to subgraph $K_s \in \Kc$.
Then the set $\{a_{ijs}(x), x \in V \cup E, i \in [|\Rc|], j \in [N], k \in [||V|+|E|]\}$ characterizes completely the sequence of rule applications and the graphs to which they were applied.
In other words, by reading the sequence of $a_{ijs}$'s, we can tell what rule was applied when to what subgraph.

When examining the effect of a rule application on a given element $x \in V \cup E$, we must give the rule $R_i$, the subgraph $K_s$ to which it applies, and the role played by $x$ in that subgraph.
Given a vertex $v$, the triplet $(k,i,s)$ says that $v$ plays role $k$ for rule $R_i$ in subgraph (or `stage') $K_s$.
A vertex may have many such triplets since it may be shared by many subgraphs and play different roles in them for different rules.
Same goes for edges.
Then we define the function $\rho: V \cup E \rightarrow 2^{\Ne \times \Ne \times \Gc}$ by 
\begin{equation}
\rho(x) = \{(k,i,s) \; s.t. \; x \textrm{ plays role $k$ for rule $R_i$ in subgraph }K_s\}
\end{equation}
In what follows we write
\[\rho_1(x) = \{k \in \Ne \; s.t. \; \exists (k,i,s) \in \rho(x)\}\]
\[\rho_2(x) = \{i \in \Ne \; s.t. \; \exists (k,i,s) \in \rho(x)\}\]
\[\rho_3(x) = \{s \in \Ne \; s.t. \; \exists (k,i,s) \in \rho(x)\}\]

\subsection{Data for a rule}
For a rule $R_i$, we need to know
\begin{itemize}
	\item The roles it disables when applied to $H_R$: this is given by $<i>$
	\item The induced subgraphs it applies to in $G$: let this be $\Kc(i)$
\end{itemize}

\section{Disabling of rules}
\label{disablingOfRules}
When a rule is applied, it changes the graph, and this affects the applicability of the rules to the resulting graph. 
For example, if a rule deletes a vertex, then that vertex can not have any rule applied to it from that point onwards. 
As an example, consider $H_{R_i} = v_1e_1v_2e_2v_3e_3v_4$, and the rule fuses $e_2$ to $e_3$ so $R(H_{R_i}) = v_1e_1v_2e^+v_4$.
Then the effect of this rule is that $e_2$ and $e_3$ can no longer play any role from that point onwards (in any rule in any subgraph) since they've disappeared. 
Same for $v_3$ which linked them.
If roles($e_2,e_3,v_2$) = $4,5,6$ then we define $<i> = \{4,5,6\}$ to be the set of roles that are disabled forever by an application of this rule $R_i$.
More generally, a rule applied to an element (strictly, to a subgraph containing that element in a particular role) implies that this element can no longer play any role in any subgraph for any rule.

Note that we don't try to model now what role might be played by the new edge $e^+$, since this would complicate things tremendously.
Note also that instead of introducing a new edge $e^+$ we could've just modeled this as the survival of $e_2$, i.e. $R(H_{R_i}) = v_1e_1v_2e_2v_4$. 

\subsection{Disabling by structure change}
When a rule is applied on a particular subgraph $K_s$, it disables forever its vertices and edges whose roles are listed in $<i>$.
This list is given by:
\[F_{i,s} = \{x \in K_s \;|\; \textrm{role}(x,i) \in <i>\}\]
These elements $x$ also played other roles for other rules in other subgraphs.
Those are the subgraphs listed in $\rho_3(x)$.
The conservative thing to do then is to assume that those other subgraphs no longer exist as structures, and thus should be disabled or `destroyed'.
\footnote{This is not the most accurate thing to do since the new edge $e^+$ (or the surviving edge $e_2$) might save the situation but that's too comlicated.}
Therefore we define the set of subgraphs destroyed by the application of rule $R_i$ to be 
\begin{equation}
\label{eq:Di}
\forall R_i \in \Rc, D(i) := \{s \in \rho_3(x) \;|\; \text{roles}(x) \in <i>\}
\end{equation}

The disabling action of the rules can now be stated as
\begin{equation}
\label{eq:disabling}
\forall i,j,s \; a_{ijs} =1 \implies a_{i'j's'} = 0 \;\forall \; i', j'>j,s' \in D(i)
\end{equation}

\subsection{Disabling by parameter changes}
Another way in which a rule might affect the application of future rules is by its effect on the automata parameters.
Let $P_x[0]$ be the initial value of the parameter vector $P_x$ (i.e., before any rules application).
Let $P_x[j]$ be its value at time $j$ after $j$ rule applications.
So the rule to be applied at time $j$ uses the value $P_x[j]$ to determine its applicability.

In general, a rule application might update the parameters of an element $x$.
We postulate that 
\begin{enumerate}
	\item [[Locality of Parameter Update]] (LoPU) When a rule is applied on a subgraph $K$ containing $x$, the parameter $P_x$ is updated using the values of $x$'s co-actors only. 
	That is, the parameters $P_y$ of $y \in V(K)\cup E(K)$ only.
	\label{LoPU}
\end{enumerate}

The form of the update depends on the rule and the role of the element in that rule.
So in the equation that follows, we index the update function $f_{ik}$ by the rule $R_i$ and the role $k=role(x,R_i)$.
Since only the rule applied at the previous step should play a part in the update, we pre-multiply $f_{ik}$ by $a_{i,j-1,s}$ which tells us which rule was applied.
Since this rule application matters only if $x$ is actually part of the stage $K_s$ on which the rule is applied, we also pre-multiply by the indicator function $\mathbf{1}_{\{K_s\}}(x)$ (which equals 1 only if $x\in K_s$ and is 0 otherwise.)
Since the assumption \ref{LoPU} says that only parameters from co-actors affect $P_x$, only the co-actors appear as arguments to $f_{ik}$.
Note that $x$ itself therefore appears in the argument.
The general form of the udpate is
\begin{eqnarray}
\label{eq:paramUpdate}
&& \forall x, j
\\
&& P_x[j] =  \sum_{i,s}a_{i,j-1,s} \mathbf{1}_{\{K_s\}}(x) f_{i,role(x,i)}(P_y[j-1],y \in V(K_s)\cup E(K_s))
\nonumber
\end{eqnarray}

Function $f_{i,k}$ will take the form either min, max or sum.

The following axioms we assume for rule applications:
\begin{enumerate}
	\item [[Sanity]] If $G$ is physiological (i.e. is a physiologically meaningful model of the heart), then $R(G)$ is physiological. This is a sanity requirement on our rules.
	\label{axiomSanity}
	\item [[Permanence]] Once a stage $K$ is destroyed by the application of a rule $R_i$, it is destroyed forever.
	Thus, if a vertex is modified in such a way that a rule $R_i$ can't be applied to it \emph{in role $k$} at some step, no future rule applications will make $R_i$ applicable to it again.
	\label{axiomPermanence}
	\item [[Time-Invariance (TI)]] The effect of a rule on the structure of a graph does not depend on when the rule was applied.
	E.g., if a rule merges two vertices, then this effect is the same regardless of whether the rule was applied at step $j$ or step $j'$.
	\label{axiomTI}
	\item [[Space-Invariance (SI)]] The effect of a rule on a vertex does not depend on the specific subgraph on which the rule is applied. 
	Rather it only depends on the role.
	E.g., if a rule merges a vertex with one of its neighbors, it does so regardless of the subgraph it is currently being applied to. 
	(We could have achieved the same effect by defining the rule directly as a function of equivalence classes induced by isomorphism to $H_R$).
	\label{axiomSI}
\end{enumerate}

\section{Expressing model appropriateness for the requirement}

Recall that we seek a model that is compatible with the requirement $\phi$.
This implies that the truth value of every atomic proposition appearing in the spec $\phi$ can be evaluated on any run of the model.
Let $AP_\phi$ be the set of atomic propositions appearing in $\phi$.
In general, the set $AP_\phi$ will contain propositions involving the edges and vertices of the model $G$ and their dynamics. 
Therefore, for compatibility, the final model should preserve the edges and vertices appearing in $AP_\phi$. 
Let $V_\phi$ and $E_\phi$ be those vertices and edges.
They are preserved if no rule involves them in any role.
This is expressed as
\begin{equation}
\label{eq:Vphi}
\forall j, \forall i, \forall s \; s.t. \; K_s \cap (V_\phi \cup E_\phi)\neq \emptyset, a_{ijs}=0
\end{equation}

\section{Interdependence between rules}
We can now express the interdependence between the rules. 
(Never mind the numbering)

1) First, we need to express that only one rule is applied at a step, and to one stage:
\begin{equation}
\label{eq:oneruleinstepArithm}
\forall j, \; \sum_{i,s}a_{ijs}  \leq 1\; \forall j,k,v
\end{equation}

2) A rule is applied only on a subgraph subject to it:
\begin{equation}
\label{eq:ruleongraph}
\forall j,i,s \notin \Kc(i): a_{ijs} = 0
\end{equation}

6) We need to express that a rule is applied at every step
\begin{equation}
\label{eq:oneruleeverystepArithm}
\forall j\; \sum_{i,s}a_{ijs} \geq 1 
\end{equation}
Note that these can be combined into:
\begin{equation}
\label{eq:exactlyoneArithm}
\forall j\; \sum_{i,s \in \Kc(i)}a_{ijs} = 1 
\end{equation}


4) We need to express rule disabling by structure change, so we arithmetize \eqref{eq:disabling}.
\begin{equation}
\label{eq:disablingStructArithm}
\forall i,j,s \; a_{ijs}\left(\sum_{i,j'>j,s' \in D(i)}a_{i'j's'}\right) =0
\end{equation}

7) We need to express rule precedence, namely that some rules $R_i$ require that other rules from a set $\pi(i)$ be applied first:
\begin{eqnarray}
\label{eq:precedenceArithm}
&& \forall i,j,s, a_{ijs}=1 \implies a_{i'j's'}=1 \textrm{ for some } j'<j,s',\forall i'\in \pi(i)
\nonumber
\\
\Leftrightarrow && \forall i,j,s, a_{ijs}=1 \implies \sum_{j'<j,s'}\left(\Pi_{i'\in \pi(i)}a_{i'j's'}\right) \geq 1 
\nonumber
\\
\Leftrightarrow && \forall i \sum_{j,s}a_{ijs} \geq 1 \implies \sum_{j'<j,s'}\left(\Pi_{i'\in \pi(i)}a_{i'j's'}\right) \geq 1 
\nonumber
\\
\Leftrightarrow && \forall i, \sum_{j,s}\left(a_{ijs} + \sum_{j'<j,s'}\left(\Pi_{i'\in \pi(i)}a_{i'j's'}\right)\right) \neq 1 
\end{eqnarray}

8) Conditions for applying a rule to a graph: since the parameter values change (potentially) with every step $j$, we reformulate and then arithmetize \eqref{eq:applicableR} as follows
\begin{eqnarray}
\label{eq:applicableRArithm}
&& \forall j,i,K \equiv H_{R_i}, R_i(K) \textrm{ is defined only if } P_K[j] \models \phi_{R_i}
\nonumber
\\
\Leftrightarrow && \forall j,i,s, a_{ijs}=1 \implies B_iP_{K_s}[j]-C_i \leq 0 
\nonumber 
\\
\Leftrightarrow && \forall j,i,s, a_{ijs} (B_iP_{K_s}[j]-C_i) \leq 0 
\end{eqnarray}

9) Parameter updates were already arithmetized above in \eqref{eq:paramUpdate}. 
We give a slightly different but equivalent formulation here
\begin{eqnarray}
\label{eq:paramUpdate2}
&& \forall x, j, i
\\
&& P_{x}[j;i] =  \sum_{s}a_{i,j-1,s} \mathbf{1}_{\{K_s\}}(x) f_{i,role(x,i)}(P_y[j-1;i],y \in V(K_s)\cup E(K_s))
\nonumber
\end{eqnarray}
This is more compatible with AMPL.

10) We need to express model appropriateness, so we repeat \eqref{eq:Vphi}
\begin{equation}
\label{eq:VphiArithm}
\forall j, \forall i, \forall s \; s.t. \; K_s \cap (V_\phi \cup E_\phi)\neq \emptyset, a_{ijs}=0
\end{equation}
Note we don't need to arithmetize it since its elements are static and known beforehand.

%It remains to deal with \emph{new} edges introduced by the rules, specifically by the merging of old edges (following the deletion of vertices).
%These new edges $e^+$ are treated as just another edge in the constraint inequalities, and thus have their own $r_{ijk}(e^+)$ variables.
%But because a new edge exists for part of the time and not at every step $j \in [N]$, its inequalities should apply only at the indices $j$ beyond the time they are created.
%We know beforehand which rules introduce new edges, so let that set of rules be denoted by NPR.
%At every step, a priori, any of the rules in NPR could be applied. 
%There are $N$ steps.
%So we define $|NPR| \cdot N$ binary variables $p_{ij}$. 
%Variable $p_{ij} = 1$ iff rule $R_i$ was applied in the previous step $j-1$, thus a new edge $e_{ij}^+$ exists at step $j$.
%In other words, $p_{ij} = 1$ iff $r_{i,j-1,k}(v)=1$ for some $v$ and $k$.
%Moreover, once a new edge is `born', it is part of the problem for thereon after.
%Thus, 
%\begin{equation}
%\label{eq:pij}
%\forall i\in [m], \; p_{ij} = 1 \implies p_{i,j+1} = 1 \; \forall j' > j
%\end{equation}
%
%Correspondingly, for these new edges, \eqref{eq:rijke} becomes
%\begin{equation}
%\label{eq:rijkenew}
%\forall i\in [m], j \in [N],k \in [O], \; p_{ij}\left(r_{ijk}(e_{ij}^+) + \sum_{j < j' \leq N}r_{i'j'k'}(e_{ij}^+) \right) \leq 1 \; \forall (i',k') \in [i,k]
%\end{equation}
%In what follows, $E^+$ denotes the set of new edges.

\section{A measure of abstractness}
We must define a measure of `abstractness'.
Based on the fact that a rule decreases the number of vertices and edges in the subgraph to which it is being applied, we define the abstractness of a graph $G$ as $|V(G)|+|E(G)|$.
Note this \emph{ignores the transformations made by the rules on the dynamics of the vertices and edges. We need to include that.}

We introduce a further axiom on the abstracting power of a rule:
\begin{enumerate}
	\item [[Constant Abstraction (CA)]] A rule has fixed abstraction power
	\[|V(K)| - |V(R(K))| = constant\; \delta_{R,\nu}\; \forall K \equiv H_R\] 
	\[|E(K)| - |E(R(K))| = constant\; \delta_{R,\epsilon}\; \forall K \equiv H_R\] 	
\end{enumerate}

After applying a sequence of rules $(R_l)_{l\in L}$ from the set $\Rc$ to the graph $G$, the abstractness of the final graph $G'$ is $|V'|+|E'|$, and can be calculated as 
\[|V|-\sum_{l \in L}\delta_{R_l,\nu} + |E| - \sum_{l \in L} \delta_{R_l,\epsilon}\]

At step $j$, we define the gain in abstraction to be $\delta_{j,\nu}+\delta_{j,\epsilon}$ where $\delta_{j,\nu}=\delta_{R_i,\nu}$ iff $R_i$ is applied at time $j$, i.e. iff $a_{ijs}=1$ for some $s$. 
We can further word this as $\delta_{j,\nu}=\delta_{R_i,\nu}$ iff $\sum_{s}a_{ijs}\geq 1$.
That last sum actually equals 1 (or 0) since a rule is applied to one graph at a time.

Therefore we can compute: for all $j$,
\begin{equation}
\label{eq:deltav}
\delta_{j,\nu} = \delta_{R_1,\nu} \left(\sum_{s}a_{1js}\right) + \delta_{R_2,\nu}\left(\sum_{s}a_{2js}\right) + \ldots + \delta_{R_m,\nu} \left(\sum_{s}a_{mjs} \right)
\end{equation}
\begin{equation}
\label{eq:deltae}
\delta_{j,\epsilon} = \delta_{R_1,\epsilon} \left(\sum_{s}a_{1js}\right) + \delta_{R_2,\epsilon}\left(\sum_{s}a_{2js}\right) + \ldots + \delta_{R_m,\epsilon} \left(\sum_{s}a_{mjs} \right)
\end{equation}
(Only one of the summands sums to 1, the others to 0, since only one rule is applied in a given step $j$).

\section{The most abstract model that is compatible with the requirement}

Finally, we define the optimization whose solution gives the most abstract model subject to preserving the sets $V_\phi$ and $E_\phi$.

The data of the problem is:
\begin{itemize}
	\item the graph $G = (V,E)$.
	\item The rules $\Rc = \{R_1,\ldots,R_m\}$ and associated subgraphs $H_{R_i}$
	\item For each $H_{R}$, the list of integers uniquely identifying its vertices and edges, roles($H_R$)
	\item the induced subgraphs $\Kc = \{K_1,\ldots,K_S\}$.
	\item for each $K_s$, the subgraph $H_R$ it is isomorphic to.
	\item for each $R_i$, the list $<i>$. This is a finite list of integers from the set roles($H_{R_i}$).
	\item for each $R_i$, $\pi(i)$ = list of rules preceding $R_i$. $\pi(i)$ is a list of integers from $[m]$.
	\item for each $R_i$, the list of subgraphs it applies to $\Kc(i)$
	\item $\rho(x)$ for each $x\in V\cup E$. $\rho(x)$ is a finite set of integer triplets $(k,i,s)$ where $s \leq |\Kc|$, $k \leq |V(K_s)\cup E(K_s)|$, $i \leq |\Rc|$. This can be induced from the above data.
	\item for each $R_i$,the rule application conditions $\phi_i$
	\item $f_{ik}$ functions for parameter updates
\end{itemize}

The decision variables are
\begin{itemize}
	\item The binaries $a_{ijs}$, $|\Rc|N|\Kc|$ of them ($N$ is the number of time steps)
\end{itemize}

The optimization is given by the following integer linear program over the decision variables

\begin{eqnarray}
\min_{a_{ijs}} &&|V|-\sum_{j \in [N]}\delta_{j,\nu} + |E| - \sum_{j \in [N]} \delta_{j,\epsilon} 
\\
&& \textrm{s.t. } \eqref{eq:oneruleinstepArithm},\eqref{eq:oneruleeverystepArithm},\eqref{eq:exactlyoneArithm},\eqref{eq:disablingStructArithm},\eqref{eq:precedenceArithm},\eqref{eq:applicableRArithm},\eqref{eq:paramUpdate2},\eqref{eq:VphiArithm},\eqref{eq:deltav},\eqref{eq:deltae}
\nonumber
\end{eqnarray}


\end{document}